%%% Seznam použité literatury je zpracován podle platných standardů. Povinnou citační
%%% normou pro diplomovou práci je ISO 690. Jména časopisů lze uvádět zkráceně, ale jen
%%% v kodifikované podobě. Všechny použité zdroje a prameny musí být řádně citovány.

\def\bibname{Bibliography}
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\bibname}

\bibitem{rdf}
{\sc W3C}. 
Resource Description Framework (RDF): \emph{Semantic Web Standards}.
W3C - RDF CORE WORKING GROUP. 
\emph{W3C - Semantic Web Standards} [online].
2013, 22.3.2013 [cit. 2013-05-22].
Available from: \url{http://www.w3.org/RDF/}

\bibitem{ld}
{\sc HEATH,} Tom.
LINKED DATA COMMUNITY. \emph{Linked Data: Connect Distributed Data across the Web}
[online]. 2013 [cit. 2013-02-3]. 
Available from: \url{http://linkeddata.org/}

\bibitem{dcv}
{\sc W3C.}
The RDF Data Cube Vocabulary:
\emph{W3C Candidate Recommendation 25 June 2013} [online]. 2013
[cit. 2013-07-26]. Available from: \url{http://www.w3.org/TR/vocab-data-cube/}

\bibitem{payola}
{\sc ŠIROKÝ}, Jan, Jiří HELMICH, Ondřej HEŘMÁNEK, Ondřej KUDLÁČEK and Kryštof VÁŠA.
PAYOLA. \emph{Payola} [online]. Prague, 2012 [cit. 2013-07-26]. 
Available from: \url{http://www.payola.cz/}

\bibitem{ldvm}
 {\sc FERNÁNDEZ,} Josep Maria Brunetti, Sören AUER and Roberto GARCIA.
 \emph{The Linked Data Visualization Model}
 [online]. Lleida, Spain; Leipzig, Germany, 2012
 [cit. 2013-04-13].
 Available from: \url{http://iswc2012.semanticweb.org/sites/default/files/paper_29.pdf}

\bibitem{un}
{\sc UNITED NATIONS.}
\emph{United Nations: We the peoples... A stronger UN for a better world.} [online].
New York, 2013 [cit. 2013-05-22]. 
Available from: \url{http://www.un.org/en/}

\bibitem{pubdata} 
  {\sc } GOOGLE INC.
  \emph{Google Public Data Explorer}
  [online]. 2013 [cit. 2013-04-13]. Available from: \url{http://www.google.com/publicdata/explore}

\bibitem{lod2}
{\sc UNIVERSITY OF LEIPZIG}
\emph{LOD2: Creating Knowledge out of Interlinked Data} [online]. 2013
[cit. 2013-07-26].
Available from: \url{http://lod2.eu/}

\bibitem{dbpedia}
{\sc DBPEDIA.} 
\emph{DBPedia} [online]. 2013, 2013-05-08 [cit. 2013-01-16]. 
Available from: \url{http://dbpedia.org/}

\bibitem{prefixcc}
  {\sc CYGANIAK,} Richard. DIGITAL ENTERPRISE RESEARCH INSTITUTE. 
  \emph{Namespace lookup for RDF developers}
  [online]. 2013 [cit. 2013-04-13]. Available from: \url{http://prefix.cc/}

\bibitem{lod-cloud}
{\sc CYGANIAK,} Richard a Anja JENTZSCH. LATC, DERI.
\emph{The Linking Open Data cloud diagram} [online]. 2011, 2011-09-19 [cit. 2013-07-27].
Available from: \url{http://lod-cloud.net/}

\bibitem{ldvm2}
 {\sc BRUNETTI,} Josep Maria, Sören AUER, Roberto GARCÍA, Jakub KLÍMEK and Martin NECASKY.
 The Linked Data Visualisation Model.
 \emph{AKSW Subversion Repository} [online]. 2013, č. 1 [cit. 2013-04-14].
 Available from: \url{http://svn.aksw.org/papers/2013/WWW_LDVM/public.pdf}

\bibitem{owl}
{\sc W3C.}
\emph{OWL Web Ontology Language: Overview} [online]. 2004,
2004-02-10 [cit. 2012-12-28].
Available from: \url{http://www.w3.org/TR/owl-features/}

\bibitem{wikipedia}
{\sc WIKIMEDIA FOUNDATION, Inc}
\emph{Wikipedia} [online]. 2012 [cit. 2012-11-22].
Available from:  \url{http://en.wikipedia.org/wiki/Main_Page}

\bibitem{msdn-cube}
{\sc MICROSOFT.}
\emph{MSDN Library: an essential source of information for developers} [online].
Just What Are Cubes Anyway?: A Painless Introduction to OLAP Technology.
2012 [cit. 2012-12-26].
Available from: \url{http://msdn.microsoft.com/en-us/library/aa140038%28v=office.10%29.aspx#odc\_da\_whatrcubes\_topic2}

\bibitem{sdmx}
  {\sc } SDMX INITIATIVE.
  \emph{Statistical Data and Metadata Exchange}
  [online]. 2001 [cit. 2013-04-13]. Available from: \url{www.sdmx.org}

\bibitem{iso}
 {\sc } INTERNATIONAL ORGANIZATION FOR STANDARDIZATION.
 \emph{ISO - International Organization for Standardization}
 [online]. 2013 [cit. 2013-04-13]. Available from: \url{http://www.iso.org}
 
\bibitem{isosdmx}
 {\sc} ISO 17369:2013 - Statistical data and metadata exchange (SDMX).
 INTERNATIONAL ORGANIZATION FOR STANDARDIZATION.
 \emph{ISO - International Organization for Standardization} [online]. 2013 [cit. 2013-04-13].
 Available from: \url{http://www.iso.org/iso/catalogue_detail.htm?csnumber=52500}
 
\bibitem{sdmxuserguide}
 {\sc } SDMX 2.1 User Guide.
 \emph{SDMX 2.1 User Guide}.
 Version 0.1. SDMX, 2012.
 Available from: \url{http://sdmx.org/wp-content/uploads/2012/11/SDMX_2-1_User_Guide_draft_0-1.pdf}

\bibitem{mantra}
 {\sc SHNEIDERMAN,} Ben.
 The eyes have it: A task by data type taxonomy for information visualizations.
 \emph{Proceedings 1996 IEEE Symposium on Visual Languages: proceedings,
 August 14-16, 1996, Blue Mountain Lake, New York}
 [online]. Los Alamitos, Calif.: IEEE Comput. Soc. Press, 1996, s. 336-343
 [cit. 2013-04-13]. ISSN 0-8186-7469-5. DOI: 10.1109/VL.1996.545307.
 Available from: \url{http://ieeexplore.ieee.org/lpdocs/epic03/wrapper.htm?arnumber=545307}

\bibitem{olap2dc-paper}
{\sc SALAS,} Percy E, Michael MARTIN and Fernando Maia Da MOTA.
OLAP2DataCube: An Ontowiki Plug-In for Statistical Data Publishing.
\emph{Proceedings of the 2nd Workshop on Developing Tools as Plug-ins.} 
[online]. 2012, Pages: 79-83 [cit. 2013-07-26]. ISBN:9781467318204.
Available from: \url{http://www.inf.puc-rio.br/~casanova/Publications/Papers/2012-Papers/2012-TOPI-olap.pdf}

\bibitem{tabels-web}
{\sc CTIC.}
\emph{Tabels: Make meaning of tabular data} [online]. [cit. 2012-12-20].
Available from: \url{http://idi.fundacionctic.org/tabels/}

\bibitem{aksw}
{\sc ARNDT, Natanael.} AKSW. 
\emph{Agile Knowledge Engineering and Semantic Web (AKSW)} [online].
2013, 03-2013 [cit. 2013-07-26].
Available from: \url{http://aksw.org}

\bibitem{ontowiki}
{\sc TRAMP,} Sebastian. AKSW.
\emph{OntoWiki: a tool providing support for agile, distributed knowledge engineering scenarios.}
[online]. [cit. 2013-01-04]. 
Available from: \url{http://aksw.org/Projects/OntoWiki.html}

\bibitem{highcharts}
{\sc HIGHSOFT SOLUTIONS AS.}
\emph{Highcharts: Interactive JavaScript charts for your webpage} [online]. 2012
[cit. 2013-07-19]. 
Available from: \url{http://www.highcharts.com/}

\bibitem{lodspeakr}
{\sc GRAVES,} Alvaro. 
\emph{Lodspeakr: Framework to create Linked Data-based applications} [online].
2013 [cit. 2013-04-12]. 
Available from: \url{http://alangrafu.github.io/lodspeakr/}

\bibitem{angularjs}
{\sc GOOGLE.}
\emph{AngularJS: Superheroic JavaScript MVW Framework} [online]. 2011
[cit. 2013-07-01]. Available from: \url{http://angularjs.org/}

\bibitem{geoglobe}
{\sc I2G.}
\emph{Geoglobe} [online]. 2012 [cit. 2013-05-14].
Available from: \url{http://data.i2g.pl/insigos/hz-geo/globe/}

\bibitem{d3}
{\sc BOSTOCK}, Michael. 
\emph{D3.js: Data-Driven Documents} [online]. 2012 [cit. 2013-02-02].
Available from: \emph{http://d3js.org/}

\bibitem{prefuse}
\emph{Prefuse: information visualization toolkit} [online]. 2012, 2012-01-13 [cit. 2013-05-28].
Available from: \url{http://prefuse.org/}

\bibitem{tabulator-paper}
{\sc BERNERS-LEE,} Tim, Yuhsin CHEN, Lydia CHILTON, Dan CONNOLLY,
Ruth DHANARAJ, James HOLLENBACH, Adam LERER and David SHEETS.
Tabulator: Exploring and analyzing linked data on the semantic web.
 [online]. 2006 [cit. 2013-07-26]. 
Available from: \url{http://student.bus.olemiss.edu/files/conlon/others/others/semantic%20web%20papers/Berners-Lee.pdf}

\bibitem{exploratory-search}
{\sc Marchionini,} G. \emph{Exploratory search: From finding to 
understanding.} Comm. Of the ACM, 49(4), 2006.

\bibitem{explorator}
{\sc ARAÚJO,} Samur F. C. de and Daniel SCHWABE.
Explorator: a tool for exploring RDF data through direct  manipulation. 
\emph{LDOW 2009 Proceedings} [online]. 2009, s. 2009 [cit. 2013-04-08].
Available from: \url{http://events.linkeddata.org/ldow2009/papers/ldow2009_paper2.pdf}

\bibitem{sesame}
{\sc ADUNA.}
\emph{OpenRDF.org: home of Sesame} [online]. 2012 [cit. 2013-07-15].
Available from: \url{http://www.openrdf.org/}

\bibitem{mit-simile}
{\sc MIT.}
\emph{SIMILE Widgets: Free, Open-Source Data Visualization Web Widgets, and More}
[online]. 2009 [cit. 2013-06-29]. 
Available from: \url{http://simile-widgets.org/}

\bibitem{exhibit}
{\sc SMITH,} MacKenzie and Eric Miller ZEPHEIRA.
Exhibit 3.0:
\emph{An Open Source Software Platform for Publishing Linked Data}.
In: \emph{emanticweb.com: The Voice of Semantic Web Business} [online].
2011 [cit. 2013-04-26].
Available from: \url{http://semanticweb.com/exhibit-3-0-part-1-an-open-source-software-platform 
-for-publishing-linked-data_b22962}

\bibitem{ckan}
 {\sc OPEN KNOWLEDGE FOUNDATION.}
 The open source data portal software
 \emph{Comprehensive Knowledge Archive}
 [online]. 2013
 [cit. 2013-04-14]. Available from: \url{http://ckan.org/pic03/wrapper.htm?arnumber=545307}

\bibitem{thedatahub}
 {\sc OPEN KNOWLEDGE FOUNDATION.}
The Datahub:
 \emph{The easy way to get, use and share data}
 [online]. 2012
 [cit. 2013-04-14]. Available from: \url{http://datahub.io}

\bibitem{void}
{\sc ALEXANDER,} Keith, Richard CYGANIAK, Michael HAUSENBLAS and Jun ZHAO. W3C.
\emph Describing Linked Datasets with the VoID Vocabulary: W3C Interest Group Note 03 March 2011}
[online]. 2010 [cit. 2013-05-16]. 
Available from: \url{http://www.w3.org/TR/void/}

\bibitem{github-payola} 
{\sc ŠIROKÝ,} Jan, Jiří HELMICH, Ondřej HEŘMÁNEK, Ondřej KUDLÁČEK and Kryštof VÁŠA. PAYOLA.
\emph{Payola GitHub repository} [online]. 2012 [cit. 2012-10-26].
Available from: \url{https://github.com/payola/Payola}

\bibitem{github-lodstats}
{\sc AKSW.}
\emph{LODStats GitHub repository} [online]. 2012 [cit. 2013-06-06].
Available from: \emph{https://github.com/AKSW/LODStats}
 
\bibitem{lodstats}
{\sc AUER,} Sören, Jan DEMTER, Michael MARTIN and Jens LEHMANN. 
LODStats
\emph{An Extensible Framework for High-Performance Dataset Analytics.}
[online]. s. 353 [cit. 2013-07-26]. DOI: 10.1007/978-3-642-33876-2\_31.
Available from: \url{http://jens-lehmann.org/files/2012/ekaw_lodstats.pdf}

\bibitem{yahoo-pipes}
{\sc YAHOO.}
\emph{Pipes: Rewire the web} [online]. 2011 [cit. 2012-10-20].
Available from: \url{http://pipes.yahoo.com/pipes/}

\bibitem{deri-pipes}
{\sc PHUOC,} Danh Le, Christian MORBIDONI, Axel POLLERES,
Matthias Samwald Robert FULLER and Giovanni TUMMARELLO. DERI.
\emph{DERI Pipes: Open Source, Extendable, Embeddable Web Data Mashups} [online].
2011 [cit. 2012-10-12]. 
Available from: \url{http://pipes.deri.org}

\bibitem{deri-screen-source}
{\sc PHUOC,} Danh Le, Christian MORBIDONI, Axel POLLERES,
Matthias SAMWALD, Robert FULLER and Giovanni TUMMARELLO.
\emph{DERI Pipes: Open Source, Extendable, Embeddable Web Data Mashups} [online]. 2011
[cit. 2013-11-12].
Available from: \url{http://pipes.deri.org/cityfacts.html}

\bibitem{lodvis}
{\sc BRUNETTI,} Josep Maria. GRIHO.
\emph{LodVis: prototype that implements the Linked Data Visualization Model (LDVM)}
[online]. 2012 [cit. 2012-09-30].
Available from: \url{http://lodvisualization.appspot.com/}

\bibitem{virtuoso}
{\sc OPENLINK.}
\emph{Virtuoso Universal Server} [online]. 2013 [cit. 2013-01-20].
Available from: \url{http://virtuoso.openlinksw.com/}

\bibitem{payola:ug:join-plugin}
{\sc ŠIROKÝ,} Jan, Jiří HELMICH, Ondřej HEŘMÁNEK, Ondřej KUDLÁČEK a Kryštof VÁŠA. PAYOLA.
\emph{User Guide} [online]. 2012 [cit. 2013-07-27]. 
Available from: \url{https://github.com/payola/Payola/blob/develop/docs/user_guide.md#join}

\bibitem{payola:ug}
{\sc ŠIROKÝ,} Jan, Jiří HELMICH, Ondřej HEŘMÁNEK, Ondřej KUDLÁČEK a Kryštof VÁŠA. PAYOLA.
\emph{User Guide} [online]. 2012 [cit. 2013-07-27]. 
Available from: \url{https://github.com/payola/Payola/blob/develop/docs/user_guide.md}

\bibitem{squeryl}
{\sc LÉVESQUE,} Maxime. 
\emph{Squeryl: A Scala ORM for SQL Databases} [online]. 2012 [cit. 2013-02-10].
Available from: \url{http://squeryl.org/}

\bibitem{payola:dg}
{\sc ŠIROKÝ,} Jan, Jiří HELMICH, Ondřej HEŘMÁNEK, Ondřej KUDLÁČEK a Kryštof VÁŠA. PAYOLA.
\emph{Developer Guide} [online]. 2012 [cit. 2013-07-27]. 
Available from: \url{https://github.com/payola/Payola/blob/develop/docs/developer_guide.md}

\bibitem{jena}
{\scAPACHE SOFTWARE FOUNDATION.} 
\emph{Apache Jena: The core RDF API} [online]. 2011 [cit. 2013-02-27]. 
Available from: \url{http://jena.apache.org/documentation/rdf/}

\bibitem{s2js}
{\sc ŠIROKÝ,} Jan. 
\emph{SWAT: Scala Web Application Toolkit} [online]. 2012 [cit. 2013-07-27].
Available from: \url{https://github.com/siroky/Swat}

\bibitem{federated-queries}
{\sc PRUD'HOMMEAUX,} Eric and Carlos BUIL-ARANDA. W3C.
\emph{SPARQL 1.1 Federated Query: W3C Recommendation 21 March 2013} [online].
2013, 2013-03-21 [cit. 2013-07-26].
Available from: \url{http://www.w3.org/TR/sparql11-federated-query/}

\bibitem{leipzich-uni}
{\sc UNIVERSITÄT LEIPZIG.} \emph{Universität Leipzig} [online]. 2013 [cit. 2013-06-27].
Available from: \url{http://www.zv.uni-leipzig.de/}

\bibitem{playfw}
{\sc TYPESAFE.}
\emph{Play Framework: The High Velocity Web Framework For Java and Scala} [online].
2012 [cit. 2012-11-14]. 
Available from: \uri{http://www.playframework.com/} 

\bibitem{flot}
{\sc LAURSEN,} Ole. IOLA. 
\emph{Flot: Attractive JavaScript plotting for jQuery} [online]. 2007 [cit. 2013-05-06].
Available from: \url{http://www.flotcharts.org/}

\bibitem{rfc-2617}
RFC 2617.
\emph{HTTP Authentication: Basic and Digest Access Authentication}.
The Internet Society, June 1999. [online]
Available from: \url{http://tools.ietf.org/html/rfc2617}

\bibitem{apache-http-commons}
{\scAPACHE SOFTWARE FOUNDATION.}
\emph{HttpClient} [online]. 2011 [cit. 2013-04-10]. 
Available from: \url{http://hc.apache.org/httpclient-3.x/}

\bibitem{coins}
{\sc DATA.GOV.UK.}
\emph{COINS as Linked Data} [online]. 2010, 11-11-2010 [cit. 2013-01-16].
Available from: \url{http://data.gov.uk/resources/coins}

\bibitem{faceted-ldow2009}
{\sc ERLING,} Orri.
Faceted Views over Large-Scale Linked Data.  [online]. [cit. 2013-07-26].
Available from: 
\url{http://events.linkeddata.org/ldow2009/papers/ldow2009_paper3.pdf}

\bibitem{datacube-wiki}
\emph{Data cube} [online]. 2012 [cit. 2013-09-27]. 
Available from: \url{http://en.wikipedia.org/wiki/Data_cube}

\bibitem{vidax}
{\sc DUMAS,} Bruno, Tim BROCHÉ, Lode HOSTE a Beat SIGNER. ViDaX.
\emph{Proceedings of the International Working Conference on Advanced Visual Interfaces - AVI '12}
[online]. New York, New York, USA: ACM Press, 2012, s. 757-
[cit. 2013-05-12]. DOI: 10.1145/2254556.2254702.
Available from: \url{http://dl.acm.org/citation.cfm?doid=2254556.2254702}



\end{thebibliography}
