\chapter{Future work}
\label{ch:future}

Based on the restrictions of the Payola framwork mentioned in Chapter~\ref{ch:implementation}
and based on experiments with the implemented system (some of them are described in
Chapter~\ref{ch:experiments}), we learned what needs to be done in the future in order to improve
the qualities of the implemented system.

The most crucial lacking feature is a fully faceted browser. We had to adopt the 
design flaw of Payola, which is not capable of caching the results of an analysis. 
Therefore, the user is forced to work with all the results at once, which may 
cause poor performance of the system. We need the Payola framework to adopt some 
existing approaches in order to deliver such a feature. One of them was 
mentioned before --- the integration of a caching mechanism (SESAME, Virtuoso, etc.).

That will dramatically increase the capabilities of the implemented system, 
because it will be possible to work with a proper portion of the data. The user will 
be potentially able to preview the whole dataset while selecting a pattern. A 
really important fact is that the visualizers will be able to query the data 
based on the current state of the visualization, which will significantly help 
to increase the performance of the whole system. One of the features that could 
be done immediately is an improvement to the listings of the detected values of the 
Universal DCV visualizer --- also more sophisticated component than a list of 
checkboxes should be used.

In order to improve the experience of the preview, we can use some advanced 
techniques described in~\cite{faceted-ldow2009}, for instance an ordering by 
\texttt{IRI:RANK}.

Another task will be to undergo a user evaluation in order to reveal other 
missing features and imperfections. Not only based on that, we should continue 
improving the existing visualizers and introduce others for
domain--specific visualisations. The list of requested visualizers will form 
on--the--fly, while exploring other datasets. Such a process will also suggest 
other modifications to the existing visualizers. One comes to mind instantly --- we 
should be able to take advantage of more metadata, for instance measure and 
dimension datatypes, ranges, etc. It is also possible to integrate other types 
of charts.

It would be also possible to propose some procedures, which will examine a given 
dataset and try to convert it to Data Cube Vocabulary automatically. It will 
almost certainly require a more sophisticated integration with the LodVis 
project.

We will also continue to improve Payola features, which are not related with 
Data Cube Vocabulary. Based on the feedback from the ESWC 2013 conference, where the 
Inner analysis feature was presented, people found these modifications and 
features interesting and would like to use them.

Some of those improvements will require Payola to undergo a heavy refactoring, 
when the most adjusted subsystems would be the data access layer and the analytical 
pipeline evaluator.

