\chapter*{Introduction and motivation}
\addcontentsline{toc}{chapter}{Introduction and motivation}
\label{ch:preface}
Nowadays, there are many techniques of how to process data. Unfortunately, there are many
different data formats one can work with. It makes the~processing a~lot more difficult.
The task becomes even harder when one wants to connect two different datasets in order to
benefit from the~connection. The connection makes us able to get some additional information
about entities from each of the~standalone datasets. Therefore, a~lot of computation time is spent
on converting, formatting and transforming data into another form. But transforming datasets
into a~matching format is not enough. One needs to specify how the~data should be linked
together.

There are many ways of doing that. Starting with implementing the~logic into a~simple conversion
script (according to a~specific dataset) to introducing a~more complex metadata description
framework for purposes of generic data processing. Since one of the~most attractive
tasks in this area is to be able to connect any of the~datasets available on the~Internet,
we are interested in the~generic description frameworks. We would like to have 
a~tool, 
which makes us able to work with any data on the~Internet (formatted according to a~some
kind of rules). We would like to link them together, analyze them, visualize 
them.

One of the~most used description frameworks is the~Resource Description Framework~\cite{rdf}.
It is a~standard model for data interchange on the~Web. It tells us how to describe
resources on the~Internet in order to make other people, applications and tools
able to understand such a~description. That gives us the~potential to link any data on the~Internet.
Based on the~framework, a~new model named Linked Data~\cite{ld} was introduced. The model
has been brought up to make data interconnecting easier.

The result of interconnecting data while utilizing the~principles of the~Linked Data model
and Resource Description Framework is a~directed graph. Its vertices represent resources we
have information on. The edges stand for relations between such entities. From this point on,
it is up to us, how we look at the~data. We can either explore them in a~plain graph or apply
some more semantics and make domain specific visualizations while using ontologies
and other advanced techniques.

One of the~specific domains are statistical data, which are one of the~most interesting kind
of data. They are produced and processed by many stakeholders. In the~context of
Linked Open Data, the~most interesting are, of course, governments and scientific groups.
But we would like to work with such data in the~usual
way --- make tables, charts or more interesting visualizations. While speaking about Open Data, a~specific
user group --- data journalists --- would like to work with Linked Data, but they are probably
missing some basic tools, which would make them able to interpret gathered results
in the~way readers would understand.

After applying the~rules of the~Linked Data model, the~statistical data (even tabular data)
get transformed into a~generic graph. The only, but very important advantage, is that we have some additional
metadata information available. Moreover, the~data are still linked with related entities from all over the Internet.
That brings
us to another model, the~Data Cube Vocabulary~\cite{dcv}. It is a~model, which tells us how to describe
multi-dimensional (statistical) data in respect to Linked Data and RDF 
principles.

\section{Goals of the~thesis}

The aim of this thesis is to describe these models, analyze the~possibilities of 
working
with multi--dimensional data in the~environment of Linked Data. We~will also propose a~system
which will make its user able to convert Linked Data into the~Data Cube Vocabulary model.
A prototype of such a~system will be implemented. An exemplary visualisation of the~statistical
data will be implemented and presented. Moreover, some missing Payola user interface features 
will be implemented.

\section{Structure of the~text}
In Chapter~\ref{ch:statistical-data}, we describe the aforementioned 
models and standards --- RDF, Linked Data, Data Cube and Data Cube Vocabulary. 
Some examples are presented. Chapter~\ref{chap:rw} contains description of 
existing tools and applications. We compare those to our application, Payola~\cite{payola}.
We also examine some related papers, especially the LDVM proposal~\cite{ldvm}. 
The Payola application is described in Chapter~\ref{ch:payola}. Later on (Chapter~\ref{ch:proposal}),
we propose a system
for analyzing and visualizing data compliant with the Data Cube Vocabulary model.
Implementation of a prototype is described in Chapter~\ref{ch:implementation}.
In Chapter~\ref{ch:experiments}, we present capabilities of the implemented system
and~experiment with some statistical datasets.